### 2019-03-30 stableLimit.tex
change stableLimit.tex

%---The preamble----------------------
\documentclass[12pt, a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{stackrel}
\usepackage{autonum}
\usepackage[utf8]{inputenc}
\usepackage{comment}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{innerasp}{Assumption}
\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
\numberwithin{equation}{section}

@@

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson process without 2rd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ denote a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function. 
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ its left and right principle eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u 
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and  the matrix $E(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s) 
	= (M - E(\mathbf s))(\mathbf 1 - \mathbf s), 
	\quad \mathbf s \in \mathbb R_+^d.
\]
	Then \cite{GoldsteinHoppe1978Critical} shows that, if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{Pr}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha 
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha, 
\]
	and for each $\mathbf j \in \mathbb N_0^d$
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)}.
\]
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.  
	Vatutin \cite{Vatutin1977Limit} also considered analogue results for the continuous time mutitype critical Galton-Watson processes.

@@

	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
\[ \label{eq: branching mechanism}
	\psi(x,z):= 
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy), 
	\quad x\in E, z\geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\alpha \in bp\mathscr B_E$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ s.t. $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	We refer our reader to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.

	Results paralleling to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}. 
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses when  the branching mechanism is $(x,z)\mapsto z^2$ and the spatial motion satisfies some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} refined their results for a class of critical superprocesses with general branching mechanism and general spatial motions: 
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$. 
	Suppose that its spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and its branching mechanism $\psi$ satisfies the following second moment condition:
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
	Under some other mild assumptions, it was proved by Ren, Song and Zhang \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(X_t \not \equiv 0) 
	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\} 
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$; 
	$\mathbf e$ is an exponential random variable with mean $1$; 
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$. 
	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to result \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	As a continuation of those works, it is natural to ask weather results paralleling to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} can be obtained for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	Perhaps a simpler version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements. 
	Kyprianou \cite{Kyprianou2008Continuous} considered a CSBP $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$, 
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\} 
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} generalized this result, by considering a CSBP with branching mechanism 
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z) 
	= c z^\gamma l(z), 
	\quad z\geq 0.
\] 
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$. 
	They showed that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ which verifying Grey's condition. 
	In order the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

	In this paper, we establish a result paralleling to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form 
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\gamma \in bp\mathscr B_E$, $\kappa \in bp\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$. 
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ convergence to $0$ while $t\to \infty$, and is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that 
\[
	\mathbf P_{\delta_x}( X_t \not \equiv 0) 
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t
\] 
	and for a large class of non-negative testing function $f$,
\[
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}} 
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\] 
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
	A regrously statements of the assumptions and the results are presented in the next subsection.
	Perhaps it is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.

@@

	We first set some notations.
	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all the measurable real function on $E$. 
	Define $b\mathscr E :=\{f \in r\mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $p\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $s\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\neq 0\}$. 
	Define $bp\mathscr E := b\mathscr E \cap p\mathscr E$, $bs\mathscr E:= b\mathscr E \cap s\mathscr E$, $sp\mathscr E:= s\mathscr E \cap p\mathscr E$ and $spb\mathscr E : = s\mathscr E \cap p\mathscr E \cap b\mathscr E$.	
	Denote by $\mathcal M_E$ the collection of all the measures on $(E,\mathscr E)$.
	Denote by $\mathcal M^\sigma_E$ the collection of all the $\sigma$-finite measures on $(E,\mathscr E)$. 
	In this paper, to simplify the notation, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$. 
	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$ if we want to emphasize the inner product structure of Hilbert space $L^2(dm)$.
	For any $\phi \in p\mathscr E$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
	In particular, $\mathcal M^1_E$ is the collection of all the finite measures on $E$.
	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all the Borel measurable subset of $E$.

	We now give the definition of a $(\xi, \psi)$-superprocess: 
	Let the \emph{state space} $E$ be a locally compact separable metric space,
	the \emph{underlying motion} $\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be a $E$-valued Hunt process with its life time denoted by $\zeta$, and the \emph{branching mechanism} $\psi$ being a function on $ E\times [0,\infty)$ with form of \eqref{eq: branching mechanism}.
	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  testing function $f\in bp\mathscr B_E$, we have
\[
	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
\] 
	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is defined as the unique locally bounded positive solution to the equation
\[\label{eq:FKPP_in_definition}
	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
	=\Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],
	t\geq 0, x \in E.
\]
	(In this paper, to simplify the notation, for any real function $F$ on $E\times [0,\infty)$ and real function $f$ on $E$, we simply write $F(x,f):= F(x,f(x)).$)

	Define the \emph{Feyman-Kac semigroup} 
\[
	P^\beta_tf(x) 
	= \Pi_x \big[e^{\int_0^{t\wedge \zeta} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
	\quad t\geq 0, x\in E, f\in b\mathscr B_E.
\]
	(Notice that if $\beta \equiv 0$, then $P_t:= P^\beta_t$ is the \emph{transition semigroup} of process $\{\xi; \Pi\}$.) 
	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
	\[ \label{eq: Ygalom type result without 2rd moment}
	\mathbf P_\mu [X_t(f)]
	= \mu(P^\beta_t f),
	\quad \mu \in \mathcal M_f, t \geq 0,f \in b\mathscr B_E.
	\]
	This mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
	As it already be discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: Ygalom type result without 2rd moment}, we have to first establish the asymptotic behavior of the mean semigroup. 
	This can be done under the following assumptions on the underlying motion $\{\xi; \Pi\}$:
\begin{asp}{1}
\label{asp: 1}
	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
\[\begin{split}
	\Pi_x[ f(\xi_t)\mathbf 1_{t < \zeta} ]
	= \int_E p_t(x,y) f(y) m(dy),
	&\quad t>0, x \in E,f \in b\mathscr B_E;
	\\\int_E p_t(y,x)m(dy)
	\leq 1,	
	&\quad t>0,x\in E;
	\\\int_E \int_E p_t(x,y)^2 m(dx) m(dy)
	<\infty,
	&\quad t> 0;
\end{split}\]
	and, $x \mapsto \int_E p_t(x,y)^2 m(dy)$, $x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous on $E$.
\end{asp}

>>>>

%---The preamble----------------------
\documentclass[12pt, a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{stackrel}
\usepackage{autonum}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{innerasp}{Assumption}
\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
\numberwithin{equation}{section}

@@

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson process without 2rd moment condition:
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ denote a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denoted by $\mathbf F(\mathbf s) = (\mathbf F^{(1)}(\mathbf s), \dots, \mathbf F^{(d)}(\mathbf s))$ the offspring probability generating function,
	%new added 
	and  $\mathbf F_n(\mathbf s), \quad n>1$, its iterates. 
	%end new
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ its left and right principle eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ the vector $(1,\dots, 1)$.
	Suppose that
\[\label{eq: regularly varying condition for multitype branching process}
	\mathbf v E(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\]
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; and  the matrix $E(\mathbf s)$ is defined by
\[
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - E(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\]
%	Then \cite{GoldsteinHoppe1978Critical} shows that, 
Then \cite{GoldsteinHoppe1978Critical} showed that,
	if we let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F_n(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ the vector $(0,\dots, 0)$, then for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\[ \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{} (\mathbf i \cdot \mathbf u)^\alpha / \alpha,
\]
	and for each $\mathbf j \in \mathbb N_0^d$
\[\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)}.
\]
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order the left side of \eqref{eq: conditioned normalized multitype branching process} has a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogue results for the continuous time mutitype critical Galton-Watson processes.

@@

	The main process of interest in this article is a measure-valued Markov process with branching property known as the $(\xi, \psi)$-superprocess.
	The transition probability of such processes is determined by a Hunt process $\xi$ on a locally compact, separable, metric space $E$, and a function $\psi$ on $E \times [0,\infty)$ defined by
\[ \label{eq: branching mechanism}
	\psi(x,z):=
	- \beta(x) z + \alpha (x) z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(x,dy),
	\quad x\in E, z\geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\alpha \in bp\mathscr B_E$ and $\pi(x,dy)$ is a kernel from $E$ to $(0,\infty)$ s.t. $\sup_{x\in E} \int_{(0,\infty)} (y\wedge y^2) \pi(x,dy) < \infty$.
	We refer our readers to \cite{Li2011Measure-valued} for a classical reference of superprocesses.
	$\xi$ and $\psi$ are often referred to as the spatial motion and the branching mechanism.

	Results paralleling to \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} have been obtained for some critical superprocesses by Evans and Perkins \cite{EvansPerkins1990Measure-valued} and Ren, Song and Zhang \cite{RenSongZhang2015Limit}.
	Evans and Perkins \cite{EvansPerkins1990Measure-valued} considered critical superprocesses when  the branching mechanism is $(x,z)\mapsto z^2$ and the spatial motion satisfies some ergodicity conditions.
	Ren, Song and Zhang \cite{RenSongZhang2015Limit} refined their results for a class of critical superprocesses with general branching mechanism and general spatial motions:
	Let $\{(X_t)_{t\geq 0}; \mathbf P_\mu \}$ be a critical superprocess starting from a measure $\mu$.
	Suppose that its spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and its branching mechanism $\psi$ satisfies the following second moment condition:
\[\label{eq: second moment condition}
	\sup_{x\in E} \int_{(0,\infty)} y^2 \pi(x,dy)
	< \infty.
\]
	Under some other mild assumptions, it was proved by Ren, Song and Zhang \cite{RenSongZhang2015Limit} that
\[\label{eq: Kolmogorov type result with 2rd moment}
	t \mathbf P_\mu(X_t \not \equiv 0)
	\xrightarrow[t\to \infty]{} c^{-1} \langle \phi, \mu \rangle_m,
\]
	and for a large class of testing functions $f$ on $E$,
\[\label{eq: Ygalom type result with 2rd moment}
	\{ t^{-1}X_t(f); \mathbf P_\mu (\cdot | X_t \not\equiv 0)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} c \langle \phi^*, f\rangle_m \mathbf e.
\]
	Here, the constant $c > 0$ is independent of the choice of $\mu$ and $f$;
	$\mathbf e$ is an exponential random variable with mean $1$;
	and $\phi$ (respectively, $\phi^*$) is the principal eigenfunction of (respectively, the dual of) the generator of the mean semigroup of $X$.
	In \cite{RenSongSun2017Spine}, we also provided an alternative probabilistic approach to results \eqref{eq: Kolmogorov type result with 2rd moment} and \eqref{eq: Ygalom type result with 2rd moment}.

	As a continuation of those works, it is natural to ask weather results paralleling to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} can be obtained for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	%Perhaps a 	simpler
	A simpler
	version of this question has already been answered in the context of continuous-state branching processes (CSBP) which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered a CSBP $(Y_t)$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\[ \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} generalized this result, by considering a CSBP with branching mechanism
\[\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0.
\]
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a slowly varying function at $0$.
	They showed that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\[\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\]
	Later, \cite{IyerLegerPego2015Limit} considered the converse problem: Suppse that $(Z_t)$ is a CSBP with ciritical branching mechanism $\psi$ 
	%which verifying Grey's condition.
	which satisfies Grey's condition.
	In order the left side of  \eqref{eq: conditional limit of CSBP} has non-trivial weak limit for some positive function $(\lambda_t)$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

	In this paper, we establish a result paralleling to \eqref{eq: conditional limit of CSBP with stable branching} for some critical $(\xi,\psi)$-superprocess $\{X; \mathbf P\}$ with spatially dependent stable branching mechanism.
	In particular, we assume that the spatial motion $\xi$ is intrinsically ultracontractive with respect to some reference measure $m$, and the branching mechanism takes the form
\[
	\psi(x,z) = -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\]
	where $\beta \in b\mathscr B_E$, $\gamma \in bp\mathscr B_E$, $\kappa \in bp\mathscr B_E$ with $1< \gamma(\cdot )<2$, $\gamma_0 := \operatorname{ess\,inf}_{m(dx)} \gamma(x)> 1$ and $\operatorname{ess\,inf}_{m(dx)}\kappa(x) > 0$.
	We will show that $\mathbf P_{\delta_x}( X_t \not \equiv 0) $ convergence to $0$ while $t\to \infty$, and is regularly varying with index $\frac{1}{\gamma_0 - 1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that
\[
	\mathbf P_{\delta_x}( X_t \not \equiv 0)
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t
\]
	and for a large class of non-negative testing function $f$,
\[
	\{   \eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}}
	\langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\]
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} }$ and $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$.
	A regrously statements of the assumptions and the results are presented in the next subsection.
	%Perhaps it
	It
	is interesting to mention here that, even though the stable index $\gamma(x)$ is spatially dependent, the limiting behavior of the critical superprocess $(X_t)$ is primarily depended only by the lowest index $\gamma_0$.

@@

	We first set some notations.
	For any measurable space $(E,\mathscr E)$, denote by $r\mathscr E$ the colloction of all measurable real functions on $E$.
	Define $b\mathscr E :=\{f \in r\mathscr E: \sup_{x\in E}|f(x)|<\infty \}$, $p\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\geq 0\}$ and $s\mathscr E :=\{f\in r\mathscr E: \forall x\in E,~f(x)\neq 0\}$.
	Define $bp\mathscr E := b\mathscr E \cap p\mathscr E$, $bs\mathscr E:= b\mathscr E \cap s\mathscr E$, $sp\mathscr E:= s\mathscr E \cap p\mathscr E$ and $spb\mathscr E : = s\mathscr E \cap p\mathscr E \cap b\mathscr E$.	
	Denote by $\mathcal M_E$ the collection of all measures on $(E,\mathscr E)$.
	Denote by $\mathcal M^\sigma_E$ the collection of all  $\sigma$-finite measures on $(E,\mathscr E)$.
	In this paper, to simplify the notation, we write $\mu(f)$ for the integration of a function $f$ with respect to a measure $\mu$.
%	We also write $\langle f,g\rangle_m$ meaning $ \int_E fg dm$  	if we want  to emphasize the inner product structure of Hilbert space $L^2(dm)$.
    We also write $\langle f, g\rangle_m$ for $\int_E fg dm$  
    to emphasize that it is the inner product in the Hilbert space $L^2(dm)$.
	For any $\phi \in p\mathscr E$, define $\mathcal M^\phi_E:= \{\mu \in \mathcal M_E: \mu(\phi) < \infty\}$.
	In particular, $\mathcal M^1_E$ is the collection of all  finite measures on $E$.
	If $E$ is a topology space, denote by $\mathscr B_E$ the collection of all  Borel measurable subsets of $E$.

	We now give the definition of a $(\xi, \psi)$-superprocess:
	Let the \emph{state space} $E$ be a locally compact separable metric space,
	the \emph{underlying motion} $\{(\xi_t)_{t\geq 0};(\Pi_x)_{x\in E}\}$ be a $E$-valued Hunt process with its life time denoted by $\zeta$, and the \emph{branching mechanism} $\psi$ 
%	being a function on $ E\times [0,\infty)$ with form of
be a function on $E\times[0,\infty)$ given by
	\eqref{eq: branching mechanism}.
	We say a $\mathcal M^1_E$-valued Hunt process $\{(X_t); (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$ is a \emph{$(\xi,\psi)$-superprocess} if for each $t\geq 0, \mu \in \mathcal M_E^1$ and  testing function $f\in bp\mathscr B_E$, we have
\[
	\mathbf P_\mu [e^{-X_t(f)}] = e^{-\mu(V_tf)},
\]
	where the function $(t,x) \mapsto V_tf(x)$ on $[0,\infty) \times E$ is defined as the unique locally bounded positive solution to the equation
\[\label{eq:FKPP_in_definition}
	V_t f(x) + \Pi_x \Big[  \int_0^{t\wedge \zeta} \psi (\xi_s,V_{t-s} f) ds \Big]
	=\Pi_x [ f(\xi_t)\mathbf 1_{t<\zeta} ],\quad
	t\geq 0, x \in E.
\]
	(In this paper, to simplify the notation, for any real function $F$ on $E\times [0,\infty)$ and real function $f$ on $E$, we simply write $F(x,f):= F(x,f(x)).$)

	Define the \emph{Feyman-Kac semigroup}
\[
	P^\beta_tf(x)
	= \Pi_x \big[e^{\int_0^{t} \beta(\xi_r)dr} f(\xi_t)\mathbf 1_{t<\zeta}\big],
	\quad t\geq 0, x\in E, f\in b\mathscr B_E.
\]
	(Notice that if $\beta \equiv 0$,
	%then $P_t:= P^\beta_t$ is the \emph{transition semigroup} of process $\{\xi; \Pi\}$.)
	 $P_t:= P^0_t$ is the \emph{transition semigroup} of process $\xi:=\{(\xi)_{t\ge 0}; (\Pi)_{x\in E}\}$.)
	It is known, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\beta_t)$ is \emph{the mean semigroup} of the superprocess $\{X; \mathbf P\}$, in the sense that
	\[ \label{eq: Ygalom type result without 2rd moment}
	\mathbf P_\mu [X_t(f)]
	= \mu(P^\beta_t f),
	\quad \mu \in \mathcal M_f, t \geq 0,f \in b\mathscr B_E.
	\]
	This mean semigroup plays a central role in the study of the asymptotic behavior of superprocesses.
	As it already be discussed in \cite{EvansPerkins1990Measure-valued}, in order to have a result like \eqref{eq: Ygalom type result with 2rd moment} or \eqref{eq: Ygalom type result without 2rd moment}, we have to first establish the asymptotic behavior of the mean semigroup.
	This can be done under the following assumptions on the underlying motion $\{\xi; \Pi\}$:
\begin{asp}{1}
\label{asp: 1}
	There exists an $m \in \mathcal M_E^\sigma$ with full support on the state space $E$, and a family of strictly positive, bounded continuous functions $\{ p_t(\cdot,\cdot): t > 0 \}$ on $E \times E$ such that,
\[\begin{split}
	\Pi_x[ f(\xi_t)\mathbf 1_{t < \zeta} ]
	= \int_E p_t(x,y) f(y) m(dy),
	&\quad t>0, x \in E,f \in b\mathscr B_E;
	\\\int_E p_t(y,x)m(dy)
	\leq 1,	
	&\quad t>0,x\in E;
	\\\int_E \int_E p_t(x,y)^2 m(dx) m(dy)
	<\infty,
	&\quad t> 0;
\end{split}\]
	and, $x \mapsto \int_E p_t(x,y)^2 m(dy)$
%	, 
and 
	$x \mapsto \int_E p_t(y,x)^2 m(dy)$ are both continuous on $E$.
\end{asp}
